Using traffic analysis to identify The Second Generation Onion Router

### 2011-05-29 thesis/results.tex
Add in summary statistics and histograms

>>>>

Examining all of the data sets, we find the following statistics of packet
sizes:

\begin{table}[H]
  \begin{tabular}{lrrrrrr}
    \toprule
    Phase & Minimum & 1st Quartile & Median & Mean & 3rd Quartile & Max \\
    \midrule
    1 & 66 & 66 & 699 & 860.4 & 1514 & 1514\\
    2 & 66 & 66 & 652 & 760.3 & 1514 & 1514\\
    3 & 66 & 66 & 652 & 733.7 & 1514 & 1514\\
    \bottomrule
  \end{tabular}
  \caption{Summary of packet sizes}
  \label{table:packet_size_summary}
\end{table}

These statistics don't suggest much, the minimum size and 1st quartile
represent the presence of empty packets typically sent to create and destroy
connections as well as acknowledge received data. The 3rd quartile and maximum
sizes represent the maximum transmission unit for the Ethernet specification
(TODO: ref). Only the median and mean statistics suggest any difference, with
Tor traffic showing a possible preference for slightly smaller packets.
Representing each phase as a histogram however, shows a very clear distinction
between regular and Tor traffic.

\begin{figure}[H]
  \centering\includegraphics[width=\linewidth]{https_hist}
  \caption{Histogram of packet size for HTTPS traffic}
  \label{https_hist}
\end{figure}

\begin{figure}[H]
  \centering\includegraphics[width=\linewidth]{http_tor_hist}
  \caption{Histogram of packet size for HTTP traffic over Tor}
  \label{http_tor_hist}
\end{figure}

\begin{figure}[H]
  \centering\includegraphics[width=\linewidth]{https_tor_hist}
  \caption{Histogram of packet size for HTTPS traffic over Tor}
  \label{https_tor_hist}
\end{figure}

In fact, the peaks seen in each graph represent individual packet sizes, the
count for each phase is shown in table \ref{table:packet_size_summary}.

\begin{table}[H]
  \begin{tabular}{lrrrrrr}
    \toprule
    Size & HTTPS & HTTP over Tor & HTTPS over Tor \\
    \midrule
    1514 & 5,158,795 & 4,753,794 & 2,245,490\\
    652 & 347,365 & 4,452,695 & 3,082,768\\
    66 & 2,954,910 & 4,536,500 & 2,295,206\\
    \bottomrule
  \end{tabular}
  \caption{Summary of packet sizes}
  \label{table:packet_size_summary}
\end{table}
